\textsf{Are large language models superhuman chemists?}

### 2024-03-27 src/tex/ms.tex
[showyourwork] overleaf sync

>>>>

\begin{figure}
    \includegraphics{figures/overview_figure.pdf}
    \caption{\textbf{Overview of the \chembench framework.} The figure shows the different components of the \chembench framework. 
    The foundation of the framework is the benchmark corpus that consists of many questions and answers that we manually or semi-automatically compiled from various sources.
    We then used this corpus to evaluate the performance of various models and tool-augmented systems using a custom framework. To provide a baseline, we built a web application that we used to survey experts in chemistry.
    The results of the evaluations are then compiled in publicly accessible leaderboards which we propose as a foundation for the evaluation of future models.
    }
    \label{fig:overview_figure}
\end{figure}
